---
title: "lesson 10"
output: github_document
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, eval = F)
#options(tibble.print_max = 40)
```

##Set up a connection to the Olinde dataset

To start a connection:

```{r}
library(tidyverse)
conStudent <- src_mysql(
                   host = "ba-isdsclass-programdev.lsu.edu",
                  port = 3306,
                  user = 'student',
                  password = 'student',
                  dbname = "isds_3105")
conStudent
```

**If you are connecting from off-campus** you need to start the LSU client **before** you connect through R.
To start a LSU client for connecting from off-campus check [this link](https://networking.grok.lsu.edu/article.aspx?articleid=14555).


##Query a DB in dplyr

Now you can pass your connection `conStudent` to `tbl(src = ...)` to query the remote data source (a MySQL database in our case). For instance, to query the commencement table:

```{r}
commencement <- tbl(conStudent, 'commencement')
commencement
```

Note that `commencement` is not a tibble on your local machine, but a connection object to the remote source. Behind the scenes, dplyr is translating your call to the function `tbl()` into MySQL code:

```{r}
show_query(commencement)
```

Why we use connection objects instead of local dataframes? Because we want the server to compute on the server to do as much as possible before pulling any data locally to our machine. To move data from a remote to a local sorce use `collect()`. 
For instance, to create a `commencement` tibble (instead of a connection object to its remote source):

```{r}
commencementTibble <- collect(commencement)
commencementTibble
str(commencementTibble)
```

Now that we know how to query a DB using dplyr, we can use most of the dplyr join functions on our remote source. For instance, to calculate the graduates for each commencement:

```{r}
tbl(conStudent, 'graduation') %>% 
  left_join(commencement) %>% count(commencementName) 
```

And yes, you could pipe a call to ggplot and plot a barchart of total graduates by commencement:

```{r}

tbl(conStudent, 'graduation') %>% 
  left_join(commencement) %>% count(commencementName) %>% 
  ggplot(aes(x = commencementName, y = n)) +
  geom_col()
```


##Exercises

These exercises require to use mainly three different join functions: `inner_join`, `left_join` and `right_join`. To read read about how the join functions work check this [book chapter](http://r4ds.had.co.nz/relational-data.html#mutating-joins). Use the data model for the Olinde Career Center data to understand what join function is the most appropriate.

For example:

  1. Each alumnus can graduate multiple times (bachelors and masters). Thus you need to right join `alumnus` to `graduation` if you are counting LSU graduates by gender. This keeps all records from graduation and merge attributes from `alumnus` (introducing duplicates if needed)
  
  2. A college has many graduates, but each graduate belongs to only one college. Thus you may need to `left_join` graduation with `college`: You want to keep all records from graduation and merge the attributes from college. But what it some graduates do not belong to any college, and you want to ignore `NA`? Then you might use `inner_join` to merge `graduation` and `college`, which will drop those values from `graduation` that do not have a match in `college`.

1. Calculate what is the average GPA at graduation by gender.

```{r}

```

2. Calcualte what is the graduates' average GPA at graduation by ethnicity and gender

```{r}

```

3. Add a column with the number of observations for each average GPA by ethnicity and gender


4. Use `geom_density()` to plot a density plot of GPAs by gender, seting `alpha=.8`. Add title and subtitle.

```{r}

```

5. Repeat 4 facetting by college.

```{r}

```


6. Report the college with highest number of graduates (read the error message carefully if you get any: you might need to `collect()`!). 

```{r}

```

7. Calculate how many graduates are there for each major in the College of Business. Plot the output into a barchart and add a title. Use `theme()` to rotate the axis labels.

```{r}

```











