---
title: "Assignment 4"
output:
  pdf_document: default
  html_document: default
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = F, message=FALSE)
library(tidyverse)
library(lubridate)
library(scales)
library(fivethirtyeight)

```

# Trump's Tweets

Read the below dataset on from https://github.com/fivethirtyeight/data/tree/master/trump-twitter. Then use the appropriate function from the package `lubridate` to convert `created_at` into a date.

```{r}
dt <- read_csv('https://raw.githubusercontent.com/fivethirtyeight/data/master/trump-twitter/realDonaldTrump_poll_tweets.csv')
dt <- dt %>% mutate(created_at = mdy_hms(created_at))
```

Use `geom_histogram` to plot a histogram of tweets count. Change the x-axis title into 'date' and the x-axis labels into a `mon 'yy` format (e.g., `Dec '15`).

```{r}
ggplot(dt) + geom_histogram(aes(x = created_at)) +
scale_x_datetime(name = 'date', date_labels = "%b '%y")
#scale_x_datetime(name = 'date', date_breaks = '1 month', date_labels = "%b '%y") for monthly breaks
```

Note that there is a difference between time and datetime: If you coerce `created_at` to a datetime (which keeps information about the time too), you will need `scale_x_datetime` instead of `scale_x_time`


# Income map

Use the below dataset to plot a choropleth map of incomes by state. Map `median_household_income` to the state fill. For a shapefile of the US states use `map_data("state")`. Adjust the legend setting the title to "Median income" and formatting the scale as `$xx,xxx`.

```{r}
dt <- read_csv('https://raw.githubusercontent.com/fivethirtyeight/data/master/hate-crimes/hate_crimes.csv')
```

```{r}
states <- map_data("state")
mutate(dt, state = tolower(state)) %>%
  right_join(states, by = c('state' = 'region')) -> dtState
  ggplot(dtState) + geom_polygon(aes(x = long, y = lat, group = group, fill = median_household_income)) +
  coord_fixed(1.3) + 
  scale_fill_gradient(labels = dollar_format(), name = "Median Income") 
```

Repeat the above for the Deep South only (Louisiana, Alabama, Mississippi, Georgia, South Carolina). Add a title.

```{r}
dtState %>% 
filter(state %in% c("louisiana", "alabama", "mississippi", "georgia", "south carolina"))%>%
  ggplot() + geom_polygon(aes(x = long, y = lat, group = group, fill = median_household_income)) +
  coord_fixed(1.3) +
  scale_fill_gradient(labels = dollar_format(), name = "Median Income")
```

Use inline code to output the average income (appropriately formatted) and the Gini-Index for Louisiana.

```{r}
medianLA <- filter(dt, state == "Louisiana") %>% pull(median_household_income) %>% dollar()
giniLA <- filter(dt, state == "Louisiana") %>% pull(gini_index)
```

The median household income for Louisiana is `r medianLA` and the Gini-Index for Louisiana is `r giniLA`.
